\class : Problem Set \psetnum

### 2022-05-14 531_stars/pset4/solutions.tex
hw4 q4 stars

\question{\textbf{27.1 - Limit for NS vs.\ BH for rotating stars}}
\answer{}

>>>>

\question{\textbf{27.1 - Limit for NS vs.\ BH for rotating stars}}
\answer{
    The limit of stars with initial masses resulting in NSs or BHs could change due to rotation in the following ways.

    \textit{Higher mass limit:} The mass needed to create a BH would need to increase due to the increased mass loss due to rotation. This means that less mass is available to go into the creation of a remnant and so stars that would have resulted in BHs instead result in NSs.

    \textit{Lower mass limit:} However in addition to the overall mass loss, the mass of the helium core instead increases for rapidly-rotating stars due to the induced mixing. A larger core mass can also lead to the larger remnant mass and thus more easily create a BH with a given initial mass.

    Overall, I think that\dots
    \todo{Check with Emily what's more important}
}
